
\documentclass{my_cv}
\usepackage[margin=0.5in]{geometry}

\begin{document}

%create the header of the cover letter
\clhead{Adam Conn}{10965 Barbados Way}{San Diego}{CA}{92126}{aconn7395@gmail.com}{(619) 792-8677}

%create the company info
\noindent
\Large \textbf{Dynamic Biotechnology} \\
San Diego\\
92121

\vspace{0.25in}
\noindent Dear Hiring Professional,\\

\noindent
This letter is in regards to the Software Engineering position posted on Indeed under the title "Algorithms, Optics and Instrument Control".
I believe I am the candidate you are looking for to fulfill this role, and I invite you to view the accompanying resume to see how my skills and experience
align with your needs.  My current employment is with the Salk Institute where I hold many of the responsibilities listed on the job posting; particularly
with the data analysis, machine learning, and use of numpy and matplotlib. I am very content at my current position, however working with additional technology
such as Django and being involved in projects with the goal of a final product excites me.\\

\noindent
I obtained a degree in Bioengineering at UCSD in 2015. The degree had a focus on Bioinformatics and so computer science courses were
heavy in the curriculum.
I chose this area of study for many reasons, the main one being I found the interdisciplinary approach to solving problems attractive.
I first started because I had a background in biology, but I soon learned I am a computer science with an interest in Biology, and not the other
way around.  In addition to my work experience, I also teach a class two weeks a year at San Diego City College. It is a class in protein purification,
and I enjoy it very much.  I enjoy any opportunity to talk and learn about science. And I would enjoy the opportunity to talk with you further about this position.\\

\noindent
Thank you for your time and consideration!\\

\noindent
Adam Conn\\
October 18, 2016






\end{document}
